Use Of Jigsaw Puzzle Solving Algorithms In The Real World

### 2023-06-27 LaTeX_paper/paper.tex
begin rust porting

>>>>

\subsubsection{Corruption Rate Analysis}
\begin{figure}[h]
  \caption{Neighbors comparison vs Corruption rate of algorithm \ref{document:GCL}. Image taken from pater \cite{GCL} page 34.}\label{fig:GCL_Corruption_Rate}
  \centering
  \includegraphics[height=0.35\textwidth]{pictures/corruption_rate.png}
\end{figure}

From the graph \ref{fig:GCL_Corruption_Rate}, it can be observed that with a corruption rate of 0.057,
a neighbors comparison value of about 80\%
can be expected. Which means that one in every 5 connections on average will be wrong.
So in a puzzle of 500 pieces (which has approximately 1000 connections),
200 connections will be wrong on average.
It is fair to say that this is not an ideal result.

\subsubsection{Limit Match\% Analysis}
As seen earlier, the limit match percentage is \(4\%\).\newline \newline
Given that in a puzzle of N pieces there are around \(2N \) connections,
the probability of one random combination to be a
possible correct combination is: \(0.054^{2N}\).\newline \newline
The total number of possible combinations are \(N! \times 4^N\),
which means that on average, on a puzzle with \(N\) pieces,
there will be \(0.054^{2N} \times N! \times 4^N \)
possible correct combinations.\newline \newline
For \( N = 500 \) the expected number of possible combinations is around \( 1.5 \times 10^{37} \).
Which makes the chance of finding the actual correct combination basically zero.

\subsubsection{Conclusion}
In this case both the match\% and the corruption rate are bad enough to make a correct reconstruction impossible.
\newline \newline 
To lower the limit match\% is necessary to increase the threshold, but this would increase the corruption rate.
\newline \newline
To lower the corruption rate is necessary to decrease the threshold, but this would increase the limit match\%.
\newline \newline
This means that, regardless of the threshold chosen, our comparison algorithm \ref{document:my_comparator}
can not work with a state of the art solver \ref{document:GCL}.

\subsection{Solutions For The Problem}

There are two way to solve this deadlock:

\subsubsection{Improve The Comparator}

Improving the comparator can shortly be done.
Some minor improvements can be made by spending some time tweaking the current algorithm.
But it is clear that, for such a task,
the optimal solution is probably to use machine learning.

\subsubsection{Improving The Solver Algorithm}

Different algorithms have different resilience to corrupted data.
All the major algorithms that have been proposed since now, focus on speed.
It is possible that an algorithm that focuses on accuracy over speed
coud work with our comparator.

\subsubsection{The Path Forward}

Improving the comparator is probably the best long term solution,
but it comes with a problem:\newline
Manually testing if some pieces fit together, then making a scan, and finally label
them to create a dataset would require hundreds if not thousands of hours.\newline
On the other hand improving the solver is not a good solution long term,
given that it will almost certainly have a worst time complexity,
but could have some major short term benefit \newline
In particular it does not require to create a huge dataset,
and could be used to build one.
In Fact it could solve hundreds of small puzzles,
and automatically label the connections using the solution he created.
\newline\newline
Given the two options, the author of this paper has chosen to focus on improving
the solver algorithm. The choice was driven by the lack of the time needed to build a dataset,
And the belief that creating a new algorithm,
for then using that to build a dataset,
would still be faster compared to building a dataset manually.
